\newpage
\begin{thebibliography}{80}

\bibitem{}
NodeJs. \textit{Official Page}.\\
"\textbf{https://nodejs.org/en/}", ngày truy cập: 18/12/2019

\bibitem{}
Java. \textit{Official Page}.\\
"\textbf{https://docs.oracle.com/en/java/}", ngày truy cập: 18/12/2019

\bibitem{}
Python. \textit{Python 3.8.4 Documentation}.\\
"\textbf{https://docs.python.org/3/}", ngày truy cập: 18/12/2019

\bibitem{}
Django. \textit{Django documentation}.\\
"\textbf{https://docs.djangoproject.com/en/3.0/}", ngày truy cập: 18/12/2019

\bibitem{}
Flask. \textit{Flask documentation}.\\
"\textbf{http://flask.palletsprojects.com/en/1.1.x/}", ngày truy cập 18/12/2019


\bibitem{}
Sass. \textit{Official Page}.\\
"\textbf{https://sass-lang.com/}", ngày truy cập: 19/12/2019

\bibitem{}
Lesscss. \textit{Official Page}.\\
"\textbf{http://lesscss.org/}", ngày truy cập: 19/12/2019

\bibitem{}
MongoDB. \textit{MongoDB documentation}.\\
"\textbf{https://docs.mongodb.com/}", ngày truy cập: 20/12/2019

\bibitem{}
Oracle Database. \textit{Official Page}.\\
"\textbf{https://docs.oracle.com/en/database/oracle/oracle-database/19/cncpt/introduction-to-oracle-database.html}", ngày truy cập: 20/12/2019

\bibitem{}
Spring Framework. \textit{Official Page}.\\
"\textbf{https://spring.io}", ngày truy cập: 20/12/2019

\bibitem{}
MySQL. \textit{MySQL Documentation}.\\
"\textbf{https://dev.mysql.com/doc/refman/8.0/en/}", ngày truy cập: 20/12/2019

\bibitem{}
RESTful API. \textit{Official Page}.\\
"\textbf{https://restfulapi.net/}", ngày truy cập: 4/7/2020

\bibitem{}
Ian Sommerville (2010), Software Engineering , 9th Edition,, Addison Wesley

\bibitem{}
R. Elmasri and S.B. Navathe (2016). Fundamentals of Database Systems, 7th Edition, Addison-Wesley.

\bibitem{}
 Kendall and Kendall (2008), Systems Analysis and Design, 7th Edition.

\end{thebibliography}
